Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-19 docs/manuscript/manuscript.tex
fourth paragraph rough draft complete in clustering analysis.

Next, we compared the best indicies values for different algorthim solving methodlogy to determine the best cuts to comfirm that Ward.D2 is the best methodlogy.

>>>>

Next, we compared the best indices values for different algorithm solving methodology to determine the best cuts to confirm that Ward.D2 is the best methodology. Once again, we determined that Ward.D2 was the best algorithm and learned that best cut is four trees by doing analysis within the different indices values of different algorithm theories. We compared the values by choosing KL, Ratkowsky, and Marriot values to compare what is the best cut for different clustering methods.

\begin{table}[h!]
  \centering
  \begin{tabular}{c c m{7cm}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{imws} 
 & \\\bottomrule
  \end{tabular}
  \caption{Summary of explanatory variables (national averages at household level)}
  \label{tab:summary}
\end{table}
